Water desalination using polyelectrolyte hydrogel: Gibbs ensemble modeling

### 2022-09-07 gibbs.tex
minor

\subsubsection*{Molecular Dynamics}

Our MD model of the gel is a network of 16 linear polymer chains, each consisting of 30 monomer 
units. 
These polymer chains are connected to a diamond-like network by 8 crosslinking units.
This means, there are $\Ngel=16\cdot30 + 8=488$ gel monomers in the simulation box 
(see \reffig{fig:diamond}).
Each monomer unit of the network carries a negative elementary electric charge, thus 
simulating fully ionized polyacidic gel.
Except the particles in the network, the monovalent co- and counter-ions ions, 
$\cl$ and $\na$, are present in simulation box. 
The total electric charge of all the particles in the box is zero, therefore the amount 
of $\na$ ions is bigger than that of $\cl$ by the number of hydrogel units.
The entire simulation box setup employs periodic boundaries. 
This model is used in MD part of \emph{open system} and \emph{closed system} simulation.

For the MD part of emph{closed system} simulation analougous simulation box is created without any polymer monomers.

>>>>

\subsubsection*{Molecular Dynamics model}

Our MD model of the gel is a network of 16 linear polymer chains, each consisting of 30 monomer 
units. 
These polymer chains are connected to a diamond-like network by 8 crosslinking units.
This means, there are $\Ngel=16\cdot30 + 8=488$ gel monomers in the simulation box 
(see \reffig{fig:diamond}).
Each monomer unit of the network carries a negative elementary electric charge, thus 
simulating fully ionized polyacidic gel.
Except the particles in the network, the monovalent co- and counter-ions ions, 
$\cl$ and $\na$, are present in simulation box. 
The total electric charge of all the particles in the box is zero, therefore the amount 
of $\na$ ions is bigger than that of $\cl$ by the number of hydrogel units.
The entire simulation box setup employs periodic boundaries.
Coloumb interaction computed by P3M method.
This model is used in MD part of \emph{open system} and \emph{closed system} simulation.

For the MD part of \emph{closed system} simulation analougous simulation box is created without any polymer monomers to model the finite reservoir. 
The amount of $\na$ ions is equal to $\cl$.

By integration Langevin motion equation by Verlet algorithm for each particles we sample 
total energy of the system and pressure. 
Kinetic energy, bonded, non-bonded and Coloumb interaction contribute to the total energy of a system.
Pressure in the system calculated as in ref [Essmann et al., 1995, doi:10.1063/1.470117]
\todo{I do not know if it is needed, ML}

When computing MD the gel and reservoir box are essentially NVT-ensembles.

\subsubsection*{Monte Carlo model}

In the \emph{open system} system box with the gel and the monovalent co- and counter-ions ions, 
$\cl$ and $\na$ is allowed to exchange particles with infinite reservoir with constant chemical potential.

\dots

In the \emph{closed system} system two boxes one with the gel and the other with ions pairs only iare allowed to exchange particles.
